The Effect of Events on Australian Parliamentary Discussion (1851--2017)

### 2018-10-09 outputs/docs/events/paper.Rmd
Update scripts folder and add multiword corrections list
Update the front matter splitter

The percentage of stop-words in each record is reasonably consistent over time. This suggests that there is no significant difference in the quality of the parsing over time. Details of this process are provided in Appendix \@ref(stopwordsgraph). We mainly use Hansard records on a daily basis in this paper. Text is usually pre-processed before topic models are used. The specific steps that we take are to remove numbers and punctuation and to change the words to lower case. **[Need to bundle_ngrams i.e. New Zealand is new_zealand and ad valorem is ad_valorem.]** Then the sentences are deconstructed and each word considered individually.

@@

These scripts are primarily based on: the \texttt{PDFtools} package of @Ooms2018pdftools; the \texttt{tidyverse} package of @Wickham2017; the \texttt{tm} package of @FeinererHornik2018; the \texttt{lubridate} package of @GrolemundWickham2011; and the \texttt{stringi} package of @Gagolewski2018. The functions of those packages are supported by: the \texttt{furrr} package of @VaughanDancho2018; and the \texttt{tictoc} package of @Izrailev2014. The \texttt{hunspell} package of @Ooms2017 is also used to help find spelling issues. In addition to the packages already mentioned, in this step the R scripts to do this use the \texttt{tidytext} R package of @SilgeRobinson2016.

>>>>

The percentage of stop-words in each record is reasonably consistent over time. This suggests that there is no significant difference in the quality of the parsing over time. Details of this process are provided in Appendix \@ref(stopwordsgraph). We mainly use Hansard records on a daily basis in this paper. Text is usually pre-processed before topic models are used. The specific steps that we take are to: remove numbers and punctuation; change the words to lower case; and concatenate multiword names titles and phrases, such as new zealand to new_zealand. Then the sentences are deconstructed and each word considered individually.

@@

These scripts are primarily based on: the \texttt{PDFtools} package of @Ooms2018pdftools; the \texttt{tidyverse} package of @Wickham2017; the \texttt{tm} package of @FeinererHornik2018; the \texttt{lubridate} package of @GrolemundWickham2011; and the \texttt{stringi} package of @Gagolewski2018.

The functions of those packages are supported by: the \texttt{furrr} package of @VaughanDancho2018; and the \texttt{tictoc} package of @Izrailev2014.

The \texttt{hunspell} package of @Ooms2017 is also used to help find spelling issues.

In addition to the packages already mentioned, in this step the R scripts to do this use the \texttt{tidytext} R package of @SilgeRobinson2016.

And @Benoit2018 for compounding multiword expressions.
